$i$-UIP Clause Learning

### 2020-02-06 paper.tex
change figure link to PDF

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth,natwidth=610,natheight=642]{figures/clause_reduction_PDF.png}
    \caption{ Relative clause size reduction distribution. X axis indicates the relative size of difference between i-uip and 1-uip clauses (calculated as $\dfrac{|\oneUIPClause|-|\iUIPClause|}{|\oneUIPClause|}$ ) for each instance, and Y axis shows the probability density.}
     \label{fig:len_pdf}
\end{figure}
\begin{figure} \label{fig:len_compare}
    \centering
    \includegraphics[width=0.8\textwidth,natwidth=610,natheight=642]{i-uip-sizes-compare.png}
    \caption{Average clause size comparison plot. Each point in the plot represents an instance. X and Y axis shows the clause length from $\IUIP$ and 1-UIP, respectively. Each green (red) dot represents an compared instance between $\MapleBase$ and $\MapleIUIMIN$ ($\IUIPPURE$). }
    \label{fig:len_compare}
\end{figure}
\nf{ Do we need this?  We additionally looked at the 14 instances
  solved by $\IUIPMIN$ but not by 1-UIP. $\IUIPMIN$ produces smaller
  clauses for all of them with average relative reduction of 22\% and
  maximum 77\% (30 vs 135). Seven out of 14 instances has size
  relative reduction over 30\%. For the 9 instances solved by 1-UIP
  but not by $\IUIPMIN$, $\IUIPMIN$ only produce smaller clause for
  three instances and with average relative reduction of 3.3\%.}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth,natwidth=610,natheight=642]{proof_size_compare.png}
    \caption{Average optimized proof size between 1-uip and $\IUIPMIN$.}
    \label{fig:proof_compare}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{figures/clause_reduction_PDF.pdf}
    \caption{ Relative clause size reduction distribution. X axis indicates the relative size of difference between i-uip and 1-uip clauses (calculated as $\dfrac{|\oneUIPClause|-|\iUIPClause|}{|\oneUIPClause|}$ ) for each instance, and Y axis shows the probability density.}
     \label{fig:len_pdf}
\end{figure}
\begin{figure} \label{fig:len_compare}
    \centering
    \includegraphics[width=0.8\textwidth]{figures/i-uip-sizes-compare.pdf}
    \caption{Average clause size comparison plot. Each point in the plot represents an instance. X and Y axis shows the clause length from $\IUIP$ and 1-UIP, respectively. Each green (red) dot represents an compared instance between $\MapleBase$ and $\MapleIUIMIN$ ($\IUIPPURE$). }
    \label{fig:len_compare}
\end{figure}
\nf{ Do we need this?  We additionally looked at the 14 instances
  solved by $\IUIPMIN$ but not by 1-UIP. $\IUIPMIN$ produces smaller
  clauses for all of them with average relative reduction of 22\% and
  maximum 77\% (30 vs 135). Seven out of 14 instances has size
  relative reduction over 30\%. For the 9 instances solved by 1-UIP
  but not by $\IUIPMIN$, $\IUIPMIN$ only produce smaller clause for
  three instances and with average relative reduction of 3.3\%.}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{figures/proof_size_compare.pdf}
    \caption{Average optimized proof size between 1-uip and $\IUIPMIN$.}
    \label{fig:proof_compare}
\end{figure}
